RNA-seq from 4 cell populations

### 2021-07-30 deconvolution/fans4/molec_profiling.Rmd
bug fix

# Prepare all pairwise contrasts
index = combn(nlevels(info$CellType),2)

L = lapply( 1:ncol(index), function(j){

  L = getContrast( vobj, form, info, paste0('CellType', c(CT1, CT2)))

  L = as.matrix(L)
  colnames(L) = paste0(CT1, '.', CT2)

  L
})
L = do.call(cbind, L)

L = cbind(L, data.frame(GABAGLU.Other = c(1, 1, -1, -1),
                    MgAs.Other = c(-1/3, -1/3, -1/3, 1),
                    Olig.Other = c(-1/3, -1/3, 1, -1/3) ))

fitBasic = dream( vobj, form, info, L=L, BPPARAM=SnowParam(12, progressbar=TRUE))
```

```{r plotContrasts}
plotContrasts(round(L,2)) + theme(axis.text.x=element_text(angle=45, hjust=1))   
```

@@

    key = paste0(CT1, '.', CT2)

@@

  CT1 = levels(info$CellType)[index[1,j]]
  CT2 = levels(info$CellType)[index[2,j]]
  key = paste0(CT1, '.', CT2)

>>>>

lvl = rbind(levels(info$CellType)[index[1,]], levels(info$CellType)[index[2,]])
contrasts = apply(lvl, 2, function(x){
  paste0('CellType', x[1], " - CellType", x[2])
})
names(contrasts) = apply(lvl, 2, function(x){
  paste0(x[1], "_vs_", x[2])
})

contrasts['GABAGLU_vs_Other'] = "(CellTypeGABA + CellTypeGLU)/2 - (CellTypeMgAs + CellTypeOlig)/2"
contrasts['MgAs_vs_Other'] = "CellTypeMgAs - (CellTypeGABA + CellTypeGLU + CellTypeOlig)/3"
contrasts['Olig_vs_Other'] = "CellTypeOlig - (CellTypeGABA + CellTypeGLU + CellTypeMgAs)/3"

# combined contrast matrix
L = makeContrastsDream( form, info, contrasts = contrasts)

fitBasic = dream( vobj, form, info, L=L, BPPARAM=SnowParam(36, progressbar=TRUE))
```

```{r plotContrasts}
plotContrasts(round(L,2))   
```

@@

    key = paste0(CT1, '_vs_', CT2)

@@

  CT1 = levels(info$CellType)[index[1,j]]
  CT2 = levels(info$CellType)[index[2,j]]
  key = paste0(CT1, '_vs_', CT2)
